\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[left=0.55in, right=0.55in, top=0.55in, bottom=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5} % For professional icons (map, phone, envelope, github, etc.)
\input{glyphtounicode}

% Use Helvetica (Sans-serif) font for a modern, clean, and spacious look
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Colors matching the original resume (Professional Dark Blue / Navy theme)
\definecolor{primaryblue}{HTML}{1F4E79} % Deep blue for titles/icons
\definecolor{charcoal}{HTML}{333333} % Dark grey for body text
\definecolor{linkblue}{HTML}{2B6CB0} % Slate blue for links

% Set text color for the document
\color{charcoal}

% Custom section command to include icons and matching horizontal line
\newcommand{\resumeSection}[2]{
  \vspace{12pt}
  \textbf{\large\color{primaryblue}#1\hspace{0.5em}#2}
  \vspace{2pt}
  {\color{primaryblue}\hrule}
  \vspace{5pt}
}

% Ensure machine-readability for ATS parsers
\pdfgentounicode=1

% Spacing for bullet points (optimized for a clean, spacious recruiter-friendly look)
\setlist[itemize]{leftmargin=0.15in, topsep=2pt, itemsep=1.5pt, parsep=0pt, partopsep=0pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge\bfseries\color{primaryblue} Anshu} \\ \vspace{6pt}
    \small
    \color{charcoal}
    \faMapMarkerAlt\ Rohtak, Haryana \hspace{10pt}
    \faPhone*\ +91 8199820779 \hspace{10pt}
    \faEnvelope\ \href{mailto:anshuh027@gmail.com}{\color{charcoal}{anshuh027@gmail.com}} \\ \vspace{4pt}
    \faLinkedin\ \href{https://linkedin.com/in/anshu-hooda-289524282}{\color{charcoal}{linkedin.com/in/anshu-hooda-289524282}} \hspace{10pt}
    \faGlobe\ \href{https://anshuhooda.netlify.app}{\color{charcoal}{anshuhooda.netlify.app}} \hspace{10pt}
    \faGithub\ \href{https://github.com/AnshuHOD}{\color{charcoal}{github.com/AnshuHOD}}
\end{center}


%-----------PROFESSIONAL SUMMARY-----------
\resumeSection{\faUser}{Professional Summary}
\small{AI Automation Engineer specializing in architecting intelligent systems and autonomous agents to solve complex business challenges. Expert in designing end-to-end workflows and voice-first applications with a focus on seamless data integration. Committed to driving operational efficiency through innovative AI solutions.}


%-----------WORK EXPERIENCE-----------
\resumeSection{\faBriefcase}{Work Experience}

\noindent
\textbf{IIITDM Kurnool} $|$ Research Intern (IKS Project) \hfill \textbf{May 2026 -- Present}
\begin{itemize}
    \item Appointed as a Research Intern for the MoE-sponsored IKS project entitled ``Nyaya Shaastra for Computer Science Engineers,'' collaborating with a team of 4 researchers.
    \item Formulated logic mappings on the intersection of ancient Indian logic and modern computing under the SRIC department, preparing 2 major reports.
    \item Achieved 100\% of technical project milestones through systematic reviews and collaborative research logic flows.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Avani Enterprises} $|$ AI Automation Intern \hfill \textbf{Jan 2026 -- Apr 2026}
\begin{itemize}
    \item Deployed complex workflows for repetitive business processes, achieving a measurable 18\% reduction in operational latency.
    \item Implemented automation solutions using Webhooks and HTTP Requests that reduced manual data entry by 22\% (saving 10+ hours weekly).
    \item Designed and tested 3 autonomous decision-making tools to process real-time inputs, increasing operational accuracy by 15\%.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Branding Pioneers} $|$ AI Intern \hfill \textbf{Jul 2025 -- Sep 2025}
\begin{itemize}
    \item Produced 10+ custom automation pipelines using n8n and Make, enhancing campaign execution speed by 25\%.
    \item Orchestrated WhatsApp API integration via Wbiztool to automate client communication, increasing customer engagement by 30\%.
    \item Utilized Google Apps Script and Telegram Bots to streamline data workflows, reducing manual entry errors by 99\%.
\end{itemize}


%-----------TECHNICAL PROJECTS-----------
\resumeSection{\faCode}{Technical Projects}

\noindent
\href{https://hoodas-bakery.vercel.app}{\color{primaryblue}\textbf{Hooda's Bakery -- AI-Powered Order Automation \& CRM}} $|$ \textit{React, Node.js, MongoDB, Gemini API, Razorpay}
\begin{itemize}
    \item Architected a full-stack e-commerce system featuring a multilingual Google Gemini AI chatbot (BakeBot) for conversational order placement, complete with a 40-message context-retention memory and Hinglish/Punjabi support.
    \item Implemented a regex-based address parser on frontend checkout to automatically extract street names, cities, and pincodes from unstructured user chat messages, improving order accuracy.
    \item Incorporated Razorpay payment gateway (sandbox) and Nodemailer (Gmail SMTP) for automated secure checkouts, status updates, and digital HTML invoice dispatches upon successful validation.
    \item Built a secure React admin dashboard featuring JWT authentication to manage live orders, visualize incoming CRM leads (categorized by landing page vs. WhatsApp funnels), and track customer feedback.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Healthcare Management Automation} $|$ \textit{n8n, Supabase, Python}
\begin{itemize}
    \item Architected a digital hospital system to manage check-ins, eliminating 100\% of physical paperwork.
    \item Synchronized n8n workflow integrations with Supabase for real-time secure patient data storage.
    \item Wrote custom Python scripts to generate unique patient IDs and optimized overall patient registration speed by 40\%.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{Autonomous Local Business Intelligence Bot} $|$ \textit{n8n, Google Maps API, Google Sheets}
\begin{itemize}
    \item Developed a zero-human-intervention pipeline to extract lead data (emails, contact info, ratings) based on location and category.
    \item Engineered an automated scraping engine that dumps validated leads directly into a centralized CRM spreadsheet.
    \item Optimized lead generation for sales teams, eliminating hours of manual research and enabling multi-city extraction.
\end{itemize}

\vspace{6pt}
\noindent
\textbf{AI Voice Assistant for Customer Support} $|$ \textit{Millis.ai, Plivo, Python}
\begin{itemize}
    \item Engineered a voice assistant managing 50+ calls daily, contributing to a 15\% reduction in handling time.
    \item Crafted 50+ conversational prompts to ensure natural interactions and accurate handling of inquiries.
    \item Configured telephony pipelines with real-time response generation, bridging voice-first interfaces with backend databases.
\end{itemize}


%-----------EDUCATION-----------
\resumeSection{\faGraduationCap}{Education}

\noindent
\textbf{UIET (M.D.U)} $|$ B.Tech in Artificial Intelligence \& Machine Learning (AIML) \hfill \textbf{2022 -- 2026}
\begin{itemize}
    \item Maintaining an 8.4 CGPA with a focus on machine learning and data structures.
\end{itemize}

% Force a clean page break here to prevent splitting the 12th class entry across page 1 and page 2
\newpage

\noindent
\textbf{Jawahar Navodaya Vidyalaya (JNV)} $|$ Class XII (CBSE) \hfill \textbf{2021}
\begin{itemize}
    \item Secured 91.4\% in Senior Secondary Examination.
    \item Served as School Captain; led a student body of 450+, coordinating events and representing at district-level forums.
\end{itemize}


%-----------SKILLS-----------
\resumeSection{\faTools}{Skills}
\begin{itemize}[label={}]
    \small
    \item \textbf{Hard Skills}: AI Automation, Machine Learning, NLP, Python, Node.js, Express.js, React.js, Webhooks, RAG, JSON, LLMs (Gemini, Claude, GPT), NumPy, Pandas, REST APIs, Prompting
    \item \textbf{Software \& Tools}: n8n, Make, Albato, MongoDB, Supabase, Razorpay API, Vapi, Millis.ai, Retell, Wbiztool, LangChain, GitHub, Git
    \item \textbf{Soft Skills}: Project Management, Team Collaboration, Process Optimization, Client Communication
\end{itemize}


%-----------ACHIEVEMENTS-----------
\resumeSection{\faTrophy}{Achievements}
\begin{itemize}
    \item \textbf{Hackathon Recognition}: Secured 4th Place in a competitive hackathon organized by GeekHub.
    \item \textbf{Microsoft Selection}: Selected via MLSA evaluation for a technical interaction event.
\end{itemize}

%-------------------------------------------
\end{document}
```
